Cheat Sheet for PFPL

### 2016-08-16 pfpl/cheatsheet.tex
Bring up to date

\end{tabular}
\end{document}

>>>>

\subsection*{XII. Control Flow}
\subsubsection*{28 Control Stacks}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

65& 257 & $k \vartriangleright e$ & Right triangle & Evaluation state & Evaluate $e$ on $k$ \\
66& 257 & $k \vartriangleleft e$ & Left triangle & Return state & Evaluate $k$ on $e$\\
67& 258 & $\epsilon$ & Epsilon & Empty frame & Empty frame\\
68& 258 & (\textemdash) & Frame hole & Frame hole & A place to put an evaluated expression into a frame\\
69& 258 & $k;f$ & Stack with frame & Stack $k$ with frame $f$  & Stack $k$ has frame $f$ at the bottom\\
70& 259 & $k \vartriangleleft:\tau$ & Triangle colon & Stack $k$ expects value of type $\tau$ & Stack $k$ expects value of type $\tau$\\
71& 259 & $f:\tau\rightsquigarrow\tau'$ & Squiggle arrow & Transform & Frame $f$ transforms expression of type $\tau$ into expression of type $\tau'$\\
72& 261 & $s \looparrowright e$ & Loop arrow & Unravel & State $s$ goes to expression $e$ \\
73& 261 & $k \bowtie e = e'$ & Bowtie & Goes to & Stack $k$ and expression $e$ goes to expression $e'$\\

\end{tabular}
\subsubsection*{29 Exceptions}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

74& 266 & $k \blacklozenge$ & Dark left triangle & Failed & Stack $k$ is in a failed state \\

\subsection*{XIII. Symbolic Data}
\subsubsection*{31 Symbols}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

75 & 282 & $a \sim \tau$ & Tilde & Define $a$ & Define symbol $a$ as type $\tau$ \\
76 & 282 & $\Sigma$ & Sigma & Symbol context & Set of symbol definitions \\
77 & 284 & $'a$ & Quote & Symbol reference & Symbol reference \\
\end{tabular}

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\

\subsection*{XIV. Mutable State}
\subsubsection*{34 Modernized Algol}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
83 & 308 & $*a$ & Star & Reference & Get the value of $a$\\
84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
\end{tabular}

\end{document}
